Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

We also tested the explanatory power of each framework dimension by classifying articles as Low Novelty (LN) or High Novelty (HN) and, separately, as having Low Conventionality (LC) or High Conventionality (HC).  We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.  That null hypothesis was rejected for the WoS data along both dimensions. Consistent with previous analysis, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and hit articles were overrepresented in the HN category at a $p<0.001$ in all but two cases.  
The p-values, in those cases, were $0.002$ and $0.007$.  
Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS. The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.  Of the 12 tests for applied physics, the statistical significance supporting a positive relationship between hit articles and HN were all $p<0.10$, and 10 of 12 were $p<0.05$.  These tests also indicated strong support for the relationship between LN and hit articles in applied physics in a limited number of tests, with $p<0.10$ in 5 of 12 instances and $p < 0.05$ in 3 of 12 instances. These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality. More generally, we find that the dimensions most strongly related with hit articles vary across disciplines and between disciplinary and broad data sets.

>>>>

We also tested the explanatory power of each framework dimension by classifying articles as %Low Novelty (
LN %)
 or 
% High Novelty (
HN
%)
 and, separately, as 
% having Low Conventionality (
LC
%) 
or 
%High Conventionality (
HC
%)
.  We tested the null hypothesis that hits are distributed between LN and HN (LC and HC) in proportion to the total number of articles assigned to those categories.  That null hypothesis was rejected for the WoS data along both dimensions. Consistent with the findings in~\cite{uzzi_atypical_2013}, hit articles were overrepresented in the HC category in every instance of WoS data at a $p<0.001$ and also overrepresented in the HN category at a $p<0.001$ in all but two cases: the p-values in those exceptions were $0.002$ and $0.007$.  
Hits in the immunology and metabolism data were overrepresented in the HC category with the same statistical significance as for WoS. The relationship of novelty with hits in the immunology and metabolism data differed dramatically from the WoS, however, with statistically significant findings of hit articles being sometimes overrepresented in the LN category, and sometimes being underrepresented.  Of the 12 tests for applied physics, the statistical significance supporting a positive relationship between hit articles and HN were all $p<0.10$, and 10 of 12 were $p<0.05$.  These tests also indicated strong support for the relationship between LN and hit articles in applied physics in a limited number of tests, with $p<0.10$ in 5 of 12 instances and $p < 0.05$ in 3 of 12 instances. These results suggest that (1) both conventionality and novelty are strongly related to hits in the WoS, (2) the conventionality dimension is strongly related with hits in immunology and metabolism and novelty is not, (3) novelty is more strongly related with hits in applied physics than is conventionality. More generally, we find that the dimensions most strongly related with hit articles vary across disciplines and between disciplinary and broad data sets.
